\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-45pt}

%==== Profile ====%
\vspace*{-15pt}
\begin{center}
	{\Huge \scshape {Austin Hartschen}}\\
	austin@austinhartschen.com $\cdot$ (816)-752-0910\\
\end{center}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Garmin} \hfill Olathe, KS\\
\textit{Software Engineer} \hfill January 2019 | Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
        \item Active in the design and development of an internal web application built using React and a Node.js RESTful API - ultimately reducing errors in aircraft software configuration.
        \item Airframe Lead for Diamond DART. Tasked with understanding software requirements, configuring software, and implementation and integration of customer specific features.
        % \item GI 275
        % \item Software Testing
        % \item API development maybe? 
\end{itemize}
\textit{Software Engineer Intern} \hfill May 2018 | December 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Tested embedded software with internal modular testing framework, ensuring that the rigorous standards enforced by the FAA are met and exceeded.
	\item Identified and corrected bugs introduced by a large change that added support for more network connections within the Garmin Integrated Flight Deck.
	% \item Communicated status of work clearly to the team, mentor, and supervisor.
\end{itemize}
\textbf{University of Missouri - Library Technology Services} \hfill Columbia, MO\\
\textit{Student Software Developer} \hfill February 2018 | May 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed digital signage software for a Raspberry Pi that pulled images from a network drive and displayed a slideshow at campus libraries.
	\item Contributed to the implementation of an auto-complete search feature on the library\textquotesingle{}s website.
\end{itemize}
\textbf{Hy-Vee} \hfill West Des Moines, IA\\
\textit{Software Development Intern} \hfill May 2017 | August 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Collaborated with a team and began development on a cross-platform Xamarin application to aide stores and warehouses in fulfilling online grocery orders.
	\item Aided in the implementation of a library that allowed company owned devices to authenticate on each store's network.
\end{itemize}

%==== Military Experience ====%
\header{Military Experience}
\vspace{1mm}

\textbf{Missouri Air National Guard} \hfill St. Joseph, MO\\
\textit{Staff Sergeant - Aerospace Maintenance} \hfill April 2014 | Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Perform maintenance, service, and inspection of aircraft and aerospace support equipment utilizing technical data.
	\item Review maintenance forms, aircraft records, and reports to ensure accurate documentation.
\end{itemize}

%==== Projects =====%
\header{Projects}
\vspace{1mm}

\textbf{Linklist}
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Bookmark manager built with Django that allows users to quickly save, tag, and flag web pages.
\end{itemize}
\textbf{Blockchain Marketplace}
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
       \item Senior Capstone project built with a small team that provided an online peer-to-peer marketplace implemented using Flask and a blockchain as the underlying data structure.
\end{itemize}

\header{Skills}
\vspace{1mm}
\begin{tabular}{ l l }
	Languages:               & Python, TypeScript, SQL, C, Node.js, HTML, CSS \\
	Libraries, Frameworks \& Tools: & React, Django, Flask, Git, Jenkins, Docker, AWS \\
\end{tabular}
\vspace{2mm}

%==== Education ====%
\header{Education}
\textbf{University of Missouri - Columbia}\hfill\\
Bachelor of Science - Computer Science \hfill \\
Minor in Mathematics\\
\textit{GPA: 3.66}\\
 
\vspace{2mm}


% \header{Honors, Activities, and Volunteer Work}
% \vspace{-1mm}
% \begin{itemize} \itemsep 1pt
	% \item Dean’s List \hfill Spring 2014 | Present
	% \item Mizzou Alternative Breaks \hfill Thanksgiving 2015
	% \item Mizzou Computing Association \hfill Fall 2015 | Present
% \end{itemize}

\ 
\end{document}
